---
title: "Creating the ``r params$package_name`` R package"
author: "Sangwon Hyun, Tim Coleman, Francois Ribalet, Jacob Bien"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
knit: litr::render
output: litr::litr_gitbook
params:
  package_name: "flowtrend" 
  package_parent_dir: "." 
documentclass: book
---

# Introduction

This package implements `flowtrend`, a model used for smooth estimation of
mixture models across time. 

The paper preprint is [here](https://arxiv.org/abs/2504.12287):

This bookdown uses [literate
programming](https://jacobbien.github.io/litr-project/) to define the ``r
params$package_name`` R package, which implements the procedures described in
the paper.

# Overview

## Background

The documentation and package are both created using simple commands:

```{r render, eval = FALSE}
## To render full evaluation -- running all code.
litr::render("index.Rmd", output_dir = "docs/create")
```


(These are other convenient commands for a developer.)


```{r render-other, eval = FALSE}
## To render with MINIMUM evaluation -- not running code, and only defining functions.
litr::render("index.Rmd", output_format = litr::litr_gitbook(minimal_eval = TRUE),
             output_dir = "docs/create")


## To render full evaluation -- running all code.
litr::render("index.Rmd",
             output_format = litr::litr_gitbook(minimal_eval = FALSE),
             output_dir = "docs/create")


## Installing the package locally
## litr::render("index.Rmd", output_format = litr::litr_gitbook(minimal_eval = TRUE))
install.packages("~/repos/flowtrend-project/flowtrend", repos = NULL, type = "source")


## Loading the packaging
library(flowtrend)

## This is helpful for package building
litr::load_all("index.Rmd")

## Somewhat equivalent to the above litr::load_all()
my_load <- function(){
  litr::render("~/repos/flowtrend-project/index.Rmd", output_format = litr::litr_gitbook(minimal_eval = TRUE))
  devtools::load_all("~/repos/flowtrend-project/flowtrend")
}
my_load()
```



